\subsubsection{Digital Hardware Design}
\paragraph{MCU Selection}
The \textbf{STM32H7A3RITx} was selected as the central processing unit for this project. 
Prior experience with the STM32 platform, including peripheral configuration, pin assignment, and clock tree setup via STM32CubeMX, was a significant factor in this decision,as it reduced the required familiarisation time and allowed development to focus on the DSP implementation rather than the platform itself. 
The STM32 HAL further accelerates development by providing a well-documented abstraction layer for peripheral initialisation and data transfer.

The Cortex-M7 core running at up to \qty{280}{\mega\hertz} provides sufficient headroom for real-time DSP at \qty{48}{\kilo\hertz}.  
The device integrates all peripherals required by this project: 
I\textsuperscript{2}S for digital audio, I\textsuperscript{2}C for codec configuration, multiple ADC channels for CV and potentiometer inputs, GPIO for gate inputs and user controls, and PWM timers for LED driving. 
Multiple independent DMA streams allow audio buffer transfers, ADC acquisition, and peripheral communication to proceed concurrently without CPU involvement\cite{stmicroelectronicsStm32h7a3riDatasheet}.

\paragraph{Crystal}

The \textit{NDK NX2520SA-24.000000\,MHz} \cite{Ndk_08142018_NX2520SA24000000MHzB8} crystal was selected and verified for compatibility with the STM32H7 oscillator circuit following the procedure described in \cite{HowSelectCompatible2025}. 
Crystal compatibility requires a gain margin of at least 5, defined as:

\[
\text{Gain Margin} = \frac{g_{m,\mathrm{crit,max}} \cdot 5}{g_{m,\mathrm{crit}}} \geq 5
\]

where the critical transconductance $g_{m,\mathrm{crit}}$ is calculated from the crystal parameters as:

\[
g_{m,\mathrm{crit}} = 4 \cdot ESR \cdot (2\pi F)^2 \cdot (C_0 + C_L)^2
\]

With $ESR = 100~\Omega$, $F = 24~\text{MHz}$, $C_0 = 7~\text{pF}$, $C_L = 10~\text{pF}$, and $g_{m,\mathrm{crit,max}} = 1.5~\mathrm{mA/V}$ for the STM32H7 \cite[p.~107]{stmicroelectronicsStm32h7a3riDatasheet}, the resulting gain margin is $7.31$, confirming crystal compatibility.

The external load capacitors were calculated as:

\[
C_{L1} = C_{L2} = 2 \cdot (C_L - C_s) = 2 \cdot (10~\text{pF} - 3~\text{pF}) = \qty{14}{pF}
\]

where $C_s = 3~\text{pF}$ accounts for MCU pin and PCB parasitic capacitance.

\paragraph{Audio Codec Selection}
The \textbf{TI TLV320AIC3204} was selected as the audio codec for this project. 
The primary selection criterion was compatibility with the STM32H7 I\textsuperscript{2}S peripheral at \qty{48}{\kilo\hertz} with 16-bit stereo framing. 
Beyond the interface compatibility, the device was well suited to the project requirements for the following reasons:

\begin{itemize}
    \item A programmable gain amplifier (PGA) on both the ADC input and DAC output 
    paths allows software-controlled level adjustment without external components
    \item Configurable input impedance up to \qty{40}{\kilo\ohm} allows the 
    AC-coupling high-pass cutoff frequency to be pushed well below \qty{20}{\hertz}
    \item Internal LDO regulators accept a \qty{3.3}{\volt} supply and generate the 
    required \qty{1.8}{\volt} analog and digital rails internally, simplifying power 
    distribution
    \item Full runtime configurability of signal routing, gain, clocking, and power 
    management via an I\textsuperscript{2}C register interface
\end{itemize}

The main limitation encountered during its system integration was the complexity of the register map and the large number of interdependent configuration pages, which required careful sequencing during initialisation. 
TI's \textit{TLV320AIC3204 Application Reference Guide} SLAA557 \cite{TLV320AIC3204ApplicationReference2012} was the primary reference for register-level configuration. 
The \textit{TI E2E community forums} \cite{TIE2ESupport} proved additionally valuable, providing access to example initialisation sequences from other developers and direct answers to individual configuration questions.