\subsection{Digital Audio Fundamentals}
\label{sec:digital-audio-fundamentals}

Bringing audio into the digital domain introduces a set of fundamental concepts that shape every decision in the signal path, from sample rate and bit depth to latency and buffer design.

\subsubsection{Sampling}

A continuous-time audio signal $x_c(t)$ is converted to a discrete-time sequence by sampling it at regular intervals of period $T = 1/f_s$ \cite[p.~160]{oppenheimDiscretetimeSignalProcessing2014}:

\begin{equation}
x[n] = x_c(nT)
\end{equation}

The \textit{Nyquist--Shannon sampling theorem} states that a bandlimited signal with highest frequency component $f_{\max}$ can be perfectly reconstructed from its samples provided the sample rate satisfies $f_s \geq 2 f_{\max}$ \cite[p.~166]{oppenheimDiscretetimeSignalProcessing2014}\cite[p.~40]{zolzerDAFXDigitalAudio211}.

This project uses a sample rate of \qty{48}{kHz}, yielding a Nyquist frequency of \qty{24}{kHz}, which covers the full range of human hearing.

\subsubsection{Quantization}

Sampling produces a discrete-time sequence, but each sample value must also be represented with finite precision.
Quantization maps the continuous amplitude of each sample to the nearest value in a finite set of $2^B$ levels, where $B$ is the bit depth \cite[p.~218]{oppenheimDiscretetimeSignalProcessing2014}.
The difference between the true sample value and its quantized representation is the \textit{quantization error} $e[n]$:

\begin{equation}
e[n] = x_Q[n] - x[n]
\end{equation}

For a uniform $B$-bit quantizer with full-scale range $[-1, 1]$, the step size is $\Delta = 2^{1-B}$ and the error is bounded by $|e[n]| \leq \Delta/2$.
Treated as additive white noise, the resulting signal-to-noise ratio is well approximated by \cite[p.~226]{oppenheimDiscretetimeSignalProcessing2014}:

\begin{equation}
\mathrm{SNR} \approx 6 \cdot B - 1.25 \quad \text{[dB]}
\end{equation}

Each additional bit therefore contributes approximately \qty{6}{dB} of dynamic range. 
This project uses 16-bit audio throughout, yielding a theoretical SNR of approximately 90--\qty{96}{dB}, which is sufficient for the Eurorack context, where the analog signal path typically limits dynamic range well below this figure.

\subsubsection{Block-Based Audio Processing}

In a real-time audio system, the DSP does not process one sample at a time.
Instead, the audio hardware collects samples into a \textit{buffer} of fixed size $N$
and notifies the processor when a block is ready.
The processor must compute $N$ output samples before the hardware finishes filling the
next block; if it does not, the output buffer underruns and an audible glitch occurs.
%TODO citation

This block-based model is the standard operating mode of \ac{DMA}-driven audio peripherals.
The DMA engine operates in double-buffer mode, continuously filling a circular buffer of $2N$ samples; at each end of transaction it swaps memory pointers and raises an interrupt, giving the CPU a budget of exactly $N / f_s$ seconds to process one block \cite[Section~15.3.11]{stmicroelectronicsRM0433ReferenceManual2023}.

The block size $N$ directly controls the trade-off between latency and CPU efficiency.
A smaller block reduces the buffering delay contributed by the audio pipeline but increases the interrupt rate and the per-sample overhead of entering and leaving the processing callback.
A larger block amortises this overhead but adds latency equal to $N / f_s$. 
This project uses a block size of $N = 128$ interleaved stereo samples, equivalent to 64 frames per channel, yielding a single-block buffering latency of $64 / \qty{48}{\kilo\hertz} \approx \qty{1.33}{\milli\second}$.
%TODO citation