\subsubsection{RTOS, DMA, and Memory Layout}
% TODO: RTOS task structure, DMA buffer scheme, SDRAM/TCM layout
\subsubsection{RTOS Task Structure}

The firmware employs FreeRTOS with three concurrent tasks organized by priority:

\begin{table}[h]
	\caption{FreeRTOS Task Summary}
	\makebox[\textwidth][c]{%
		\begin{tabular}{|l|l|l|l|l|}
			\hline
			\textbf{Task Name} & \textbf{Priority} & \textbf{Stacksize} & \textbf{Notification Source} & \textbf{Responsibilities} \\
			\hline
			\texttt{AudioTask} & \texttt{56 - 1} & 512 & \makecell[l]{DMA \\ Transfer-complete ISR} & \makecell[l]{Audio DSP, DMA buffer I/O, \\ tape command dispatch} \\
			\hline
			\texttt{ControlInterfaceTask} & \texttt{56 - 3} & 256 & \makecell[l]{ADC \\ Conversion Complete ISR} & Calibrated CV and V/oct pitch \\
			\hline
			\texttt{UserInterfaceTask} & \texttt{56 - 4} & 256 & \makecell[l]{ADC, GPIO \\ Conversion Complete ISR \\ EXTI ISR} & \makecell[l]{LED logic, boot calibration, \\ pot/button handling} \\
			\hline
	\end{tabular}}
	\label{tab:rtos_tasks}
\end{table}

The highest-priority task, \texttt{AudioTask}, is responsible for all real-time audio processing: it initializes the codec and audio engine, then enters a perpetual loop in which it blocks on a direct-to-task notification issued by the DMA transfer-complete interrupt. 
On each wakeup it fetches a snapshot of the current parameters via \texttt{param\_cache\_fetch}, processes one half-block of audio through the tape-player, exciter, and Schroeder reverb stages, writes the result back to the DMA output buffer, and drains any pending tape-transport commands from the \texttt{tape\_cmd\_q} queue before yielding. 

The mid-priority \texttt{ControlInterfaceTask} waits on task notifications from the ADC driver and, upon wakeup, calls \texttt{control\_interface\_process} to convert raw ADC readings into calibrated CV and pitch values. 

The lowest-priority \texttt{UserInterfaceTask} initialises the WS2812 LED driver, executes the boot-time calibration routine---during which the audio and control tasks are explicitly suspended via \texttt{vTaskSuspend}---and thereafter responds to pot-movement and GPIO notifications to update the user-visible LED state and parameter mappings. 
In order to give the calibration routine the full CPU, it is handled by a binary semaphore \texttt{audioReadySemaphore} that gates the audio task until calibration has completed.

Parameter data propagated from the control and user interface tasks to the audio task bypasses FreeRTOS queuing entirely: \texttt{param\_cache} implements a lock-free shared-memory scheme in which the lower-priority tasks write individual fields using atomic store operations, and \texttt{AudioTask} reads a consistent snapshot each processing cycle via \texttt{param\_cache\_fetch}. 
This pattern avoids priority inversion and eliminates any blocking on the time-critical audio path, following the principle that real-time audio threads should never contend on a mutex~\cite{reinders2021}. 

%Lock-free shared-memory communication of this kind is well established in the real-time systems literature: Herlihy and Shavit provide a thorough theoretical grounding for wait-free and lock-free data structures~\cite{herlihy2012art}, while Butenhof gives a practical treatment of memory visibility and atomic operations in the context of concurrent C programs~\cite{butenhof1997programming}.


\subsubsection{Drivers and Peripherals}
% TODO: codec driver, ADC driver, CV input handling
\paragraph{Audio Codec Driver}

During hardware design, the versatile \textbf{TI TLV320AIC3204} stereo audio codec was chosen to handle analog-to-digital and digital-to-analog audio conversion.

The TLV320AIC3204 is a highly configurable audio codec controlled entirely through a register interface, exposing power management, input/output routing, gain stages, clocking, and pin multiplexing. It supports sample rates from 8~kHz to 192~kHz for both record and playback paths. The playback path provides programmable volume control, DSP filtering, and flexible DAC/analog mixing, while the record path supports both single-ended and differential input configurations with a digitally-controlled microphone preamplifier.

Clock generation is flexible: the internal clock can be derived from the \texttt{MCLK}, \texttt{BCLK}, or \texttt{GPIO} pins, or from an internal PLL whose input may likewise be sourced from any of these pins. The PLL accepts input clocks in the range of 512~kHz to 50~MHz, though its use is discouraged at the lowest power settings. The analog supply operates in the range of 1.5V--1.95V and the digital supply in the range of 1.26V--1.95V, with integrated LDOs accepting input voltages of 1.8V--3.6V. \cite{texasinstrumentsTlv320aic3204Datasheet}

A common MCLK of 12.288MHz is generated by STM32H7's PLL tree \ref{sec:clock}.
This is then used to derivate all needed sychronization signals via its internal clock dividers.

The TLV320AIC3204 is configured over I\textsuperscript{2}C using a thin register-access layer built on the STM32 HAL. The two primitive operations, \texttt{codec\_write\_reg} and \texttt{codec\_read\_reg}, each perform a blocking HAL transfer to the codec's 7-bit address (\texttt{0x18}), with any HAL error escalated immediately to the system \texttt{Error\_Handler}. Before initialisation, \texttt{codec\_i2c\_is\_ok} probes the bus with \texttt{HAL\_I2C\_IsDeviceReady} to confirm the device is accessible.

The \texttt{codec\_init} function executes a fixed register-write sequence to bring the codec into a known operating state. 
It begins with a software reset, then configures the clock dividers NDAC, MDAC, NADC, and MADC, whose values are selected at runtime from the \texttt{audio\_sample\_rate\_t} argument according to the relation $f_s = f_{MCLK} / (N \cdot M \cdot \text{OSR})$, with a 12.288~MHz master clock and a fixed OSR of 128. The I\textsuperscript{2}C interface is configured for 16-bit I\textsuperscript{2}S framing. 

Subsequent writes on Page~1 enable the AVDD LDO, configure headphone soft-stepping, set the microphone PGA settling delay, and establish the reference charge time. 
The signal routing writes connect the DAC outputs to the line-output drivers LOL and LOR, and route the line inputs through the PGA to the ADC. 

The sequence concludes on Page~0 by powering up the DAC and ADC blocks, setting unity gain, and unmuting all signal paths.


\begin{listing}[h]
\begin{minted}{c}
/* sample-rate-dependent dividers: fs = MCLK / (N * M * OSR) */
switch (rate) {
	case SAMPLERATE_48KHZ: n_val = 1; m_val = 2;  break;
	case SAMPLERATE_24KHZ: n_val = 1; m_val = 4;  break;
	case SAMPLERATE_8KHZ:  n_val = 1; m_val = 12; break;
	default:               n_val = 1; m_val = 2;  break;
}
codec_write_reg(0x0b, 0x80 | n_val); /* NDAC - MSB powers up divider */
codec_write_reg(0x0c, 0x80 | m_val); /* MDAC */
codec_write_reg(0x0e, 0x80);         /* DAC OSR = 128 */
\end{minted}
\caption{TLV320AIC3204 clock divider configuration}
\label{lst:codec_clk}
\end{listing}

Full register details and their respective configuration values are documented in TI's \textit{TLV320AIC3204 Application Reference Guide} SLAA557, section~5.2, pp.~96--128~\cite{TLV320AIC3204ApplicationReference2012}.

