The playback engine uses a mix of fixed-point and floating-point numbers. This design combines deterministic timing behaviour in the phase domain with numerically robust signal processing in the amplitude domain.

\paragraph{Fixed-Point Phase Accumulation}

The fixed-point phase accumulator pattern was first observed in the open-source firmware of the Mutable Instruments \textit{Clouds} Eurorack module 
\cite{pichenettesPichenettesEurorack2026}, where integer phase accumulators drive sample playback position and floating-point accumulators drive envelope shapes across multiple DSP components. 
This established pattern was adopted here, following the phase accumulator convention of Direct Digital Synthesis systems \cite[p.~49]{josephtierneDigitalFrequencySynthesizer1971}, adapted for variable-rate sample playback. 

The playback position is represented as an unsigned integer with fractional 
resolution in Q48.16 format (\texttt{uint64\_t}), updated according to

\[
	\phi[n+1] = \phi[n] + \Delta \phi ,
\]

where $\phi$ denotes the discrete phase and $\Delta \phi$ the phase increment corresponding to the desired playback rate.

The Q48.16 (48-bit fixed-point, 16-bit fractional) format was chosen over the more common Q16.16 because the integer part must be capable of addressing the full recording buffer.
At $f_s = \qty{48}{\kilo\hertz}$ and a buffer length of \qty{2.5}{\second}, the maximum playback index reaches
\[
    48000 \times 2.5 = 120{,}000 \text{ samples,}
\]
which exceeds the 16-bit integer range of $2^{16} - 1 = 65{,}535$, making a 48-bit integer part necessary.

Beyond addressing range, the fixed-point representation was chosen for the coherence it provides across the playback engine. The Q48.16 format naturally unifies phase accumulation, sub-sample interpolation, and crossfade distance comparison into a single numeric domain, avoiding explicit casts and \texttt{floor} operations at the boundaries between these subsystems.
Index extraction and boundary comparisons reduce to bit-shifts, as described in Section~\ref{sec:fixed-point-shifts}.

While double-precision floating-point accumulation would have been numerically sufficient given the short buffer durations used in this system, and would have offered greater readability, fixed-point arithmetic also provides exact wrap-around behaviour through modulo-$2^N$ overflow of unsigned integers, eliminating the need for explicit boundary checks. The choice reflects a deliberate trade-off in favour of arithmetic coherence and implementation explicitness over the convenience of floating-point.


\paragraph{Fixed-Point Format and Bit-Shift Conversions}
\label{sec:fixed-point-shifts}

Throughout the codebase the notation \texttt{\_qM.N} denotes a fixed-point format with $M$ integer bits and $N$ fractional bits packed into a single unsigned integer, abbreviated \texttt{\_qN} in variable names (e.g.\ \texttt{pos\_q48\_16} is a Q48.16 value; \texttt{fade\_acc\_q16} is Q16.16).
The $N$ fractional bits represent the sub-sample offset as an integer numerator with an implicit denominator of $2^N$.

All conversions between the fixed-point domain and ordinary integer indices or floating-point values reduce to two operations:

\begin{description}
	\item[Right-shift by $N$] extracts the integer part, discarding the fractional bits:
	\[
	\texttt{idx} = \texttt{pos\_q48\_16} \gg 16
	\quad \Longrightarrow \quad
	\texttt{idx} = \lfloor \phi / 2^{16} \rfloor
	\]
	The lower 16 bits remain in the original variable and represent the fractional sub-sample offset.
	
	\item[Left-shift by $N$] converts an integer sample count into the same unit as a Q.16 value, enabling direct magnitude comparison without division:
	\[
	\texttt{distance\_to\_end\_q16} = \texttt{samples\_left} \ll 16
	\quad \equiv \quad
	\texttt{samples\_left} \cdot 2^{16}
	\]
\end{description}


A representative use of both operations appears in the \texttt{playhead\_near\_end} predicate, which decides whether to arm the end-of-buffer crossfade.
The condition to test is whether the remaining samples in the buffer are fewer than the distance the playhead will traverse during the fade:
\[
\texttt{samples\_left} \leq \texttt{fade\_len} \times \frac{\Delta\phi}{2^{16}}
\]
Dividing by $2^{16}$ would require an integer division, which is both computationally expensive and introduces truncation. 
Instead, both sides are multiplied by $2^{16}$, yielding an equivalent integer comparison:
\[
\underbrace{\texttt{samples\_left} \ll 16}_{\texttt{distance\_to\_end\_q16}}
\;\leq\;
\underbrace{\texttt{fade\_len} \times \Delta\phi}_{\texttt{distance\_during\_fade\_q16}}
\]
This cross-multiplication is exact in 64-bit unsigned arithmetic and avoids division on the time-critical audio path.

\paragraph{Floating-Point Signal Processing}

While the phase domain is handled using fixed-point arithmetic, all audio-domain processing is performed in double-precision floating-point. This includes mixing, biquad filtering, and reverberation.

The target platform is based on an ARM Cortex-M7 microcontroller with hardware support for double-precision floating-point operations. 
The processor provides a pipelined \ac{FPU} capable of efficient multiply and accumulate operations, making floating-point digital signal processing computationally practical in real-time audio applications \cite{ArmCortexM7Processor}.

Floating-point arithmetic offers several important advantages for recursive and feedback-based structures such as IIR filters and reverberation networks. 
The wide dynamic range reduces the risk of overflow and eliminates the need for manual scaling strategies that are typically required in fixed-point implementations. 
Furthermore, coefficient design tools and DSP literature predominantly assume floating-point arithmetic, simplifying implementation and validation \cite[p.295]{lyonsUnderstandingDigitalSignal2011}.

\paragraph{Architectural Rationale}

The separation between fixed-point phase accumulation and floating-point signal processing was done to reflect the different numerical requirements of the two domains. 
The phase accumulator performs repeated integer addition over a statically bounded range -- a task for which fixed-point arithmetic is a natural fit. 

The audio processing chain, by contrast, involves recursive structures and coefficient arithmetic for which floating-point is the convention and the practical choice on a platform with hardware FPU support.

It should be noted that the fixed-point accumulator could have been replaced by a double-precision floating-point accumulator without meaningful loss of precision at the buffer sizes used in this system. 
The fixed-point representation was retained for the coherence it provides across the phase arithmetic, interpolation, and crossfade subsystems, as described in Section~\ref{sec:fixed-point-shifts}, rather than out of strict numerical necessity.