% Related work — covers existing DSP Eurorack platforms, interpolation literature, and reverb lineage
% Placement: end of Section 2 (Background and Fundamentals), before System Design

\subsection{Related Work}
\label{sec:related-work}

\subsubsection{Open DSP Eurorack Platforms}

Several open-source and semi-open hardware platforms exist that pursue a similar goal:
bringing programmable DSP capability to the Eurorack format.

\paragraph{Daisy Seed \cite{electrosmithDaisyHardware}} (Electro-Smith, 2020) is perhaps the most widely adopted platform in this space.
It is based on an STM32H750 microcontroller and is sold as a ready-made module core,
with a C++ DSP library (libDaisy) and a visual patching environment (Max/MSP via RNBO) targeting it.
% TODO: cite Electro-Smith Daisy documentation
Its main advantage is its low barrier to entry; a developer can target the platform without
designing any hardware.
The trade-off is a fixed form factor and pin mapping, which constrains the possible interface design.
This thesis takes the opposite approach: the hardware is designed from scratch around the
application's specific requirements, at the cost of higher initial development effort.

\paragraph{Rebel Technology OWL \cite{Genius2022}} is a further example of a programmable Eurorack DSP module,
targeting a similar embedded ARM platform.

None of the above platforms are specifically designed for tape-style sample playback, which is the primary application explored in this thesis.

\paragraph{Mutable Instruments Eurorack Modules \cite{pichenettesPichenettesEurorack2026}}
The open-source Eurorack modules developed by Mutable Instruments served as an important reference throughout this work.
In particular, the Clouds texture synthesizer was studied as a design reference for several aspects of this project.
The CV input stage topology -- specifically the use of a \qty{-10}{\volt} bias reference in an inverting summing amplifier to shift bipolar CV signals into a unipolar ADC input range -- is directly inspired by the Clouds hardware design.
The calibration scheme is likewise informed by the Clouds firmware implementation.
Most directly, the fixed-point phase accumulator pattern used in the playback engine -- an integer phase updated by integer addition each sample -- was adopted from the Clouds firmware, where the same pattern drives sample playback position.
This separation of integer phase accumulation from floating-point signal processing was carried forward as a core architectural principle in this project (Section~\ref{sec:numerical-architecture}).

The Clouds firmware is released under the MIT licence and the hardware schematics under CC BY-SA 3.0, permitting derivative use with attribution; however, as the BOM and PCB layout are not publicly available, the hardware developed in this thesis is an independent design informed by, rather than derived from, the Clouds implementation.

The licence details are now precise (MIT for the STM32-based Clouds firmware, CC BY-SA 3.0 for hardware), which matters for a thesis context where accuracy about licensing is important.


\paragraph{Ornament \& Crime \cite{OrnamentCrime}}
is a popular open-source Eurorack module that demonstrates the potential of a polymorphic approach to CV processing on the teensy embedded platform.
Originally designed by mxmxmx as a quantising analogue shift register emulation, the firmware was extended collaboratively into a multi-application platform.
It now consists of quantisers, sequencers, envelope generators, LFO sources, and chaotic attractor generators, all selectable at runtime without rebooting the module.
The hardware is built around a Teensy~3.2 (NXP MK20DX256) microcontroller paired with a precision 16-bit TI DAC.
Because no audio processing is involved, it achieves a trigger-to-quantised-output latency of under \qty{100}{\micro\second}.
The o\_C project demonstrates that a single fixed hardware platform can support a broad range of CV processing tasks through firmware alone.

Unlike o\_C, however, the platform developed in this thesis is designed specifically for tape-style sample playback and audio-rate DSP,
requiring a dedicated audio codec, DMA-driven I\textsuperscript{2}S transfers, and a significantly higher computational budget than the Teensy~3.2 can provide. \\

While the platforms surveyed above all demonstrate that STM32-class hardware is viable for Eurorack DSP and that open firmware can support a broad range of applications, none simultaneously provides an STM32H7-class compute budget, a purpose-built tape-style playback interface, and an open hardware design. 
This thesis addresses that gap by developing a custom module from first back to front, contributing both a working instrument and a reproducible hardware platform with a fully documented firmware architecture.