The primary objective of this thesis was the development of a fully functional, DSP-capable Eurorack synthesizer module on the STM32H7 platform.
The resulting system -- hardware, firmware, and two DSP focus points -- was built from scratch over the course of the project and verified against a defined set of functional and electrical requirements.

The hardware implementation delivers a complete Eurorack-compliant signal path: stereo audio input and output at Eurorack levels, CV and V/Oct input conditioning, gate inputs, slide potentiometers, push buttons, and a WS2812 RGB LED interface.
The analog frontend proved more challenging than anticipated during bring-up; initial attenuator values caused ADC saturation, requiring component changes, and two pin misassignments in the first PCB revision required bodge wires and firmware workarounds.
These issues are documented and corrected for the next revision.

On the firmware side, the FreeRTOS-based architecture met all real-time requirements with margin to spare.
End-to-end audio latency was measured at \qty{1.896}{ms} mean -- well within the \qty{5}{ms} target -- and the full DSP chain runs at 60--66\% CPU utilisation at $f_s = \qty{48}{\kilo\hertz}$, leaving sufficient headroom.
The lock-free parameter cache and DMA-driven audio pipeline both operated correctly under load throughout testing.

The two DSP focus points demonstrated that non-trivial real-time audio algorithms are feasible on this platform.
The tape-style playback engine with Hermite interpolation produces clean output across the tested pitch range, with substantially lower aliasing than the ZOH baseline at all upsampling ratios.
The Schroeder reverb implementation covers the full $0.1$--$5.0\,\mathrm{s}$ RT60 range and integrates cleanly into the audio processing chain.

\newpage
\subsection{Requirements Verification}
Table~\ref{tab:req-verification} summarises the verification status of all functional
requirements and constraints defined in Section~\ref{sec:system-requirements}.
\begin{table}[H]
    \centering
    \caption{Requirements verification summary}
    \label{tab:req-verification}
    \begin{tabularx}{\linewidth}{@{} l X l @{}}
        \toprule
        \textbf{ID} & \textbf{Verification} & \textbf{Status} \\
        \midrule
        FR-01 & Stereo audio input and output verified via oscilloscope loopback measurements with $\qty{10}{V_{pp}}$ Eurorack-level signals. Frequency response measured and good performance in audible range confirmed. & Pass \\
        FR-02 & End-to-end latency measured at \qty{1.896}{ms} mean, \qty{2.100}{ms} maximum -- well within the \qty{5}{ms} real-time requirement. & Pass \\
        FR-03 & Gate, CV, and V/Oct inputs mostly implemented and verified via driver tests and signal path measurements. \textit{Gate 03 input non-functional due to pin misassignment in this hardware revision.} & Partial \\
        FR-04 & Slide potentiometers and push buttons operational; verified via firmware driver tests. \textit{Slide potentiometer LEDs non-functional due to pin misassignment in this hardware revision.} & Partial \\
        FR-05 & WS2812 RGB LEDs functional via level-shifted PWM output. & Pass \\
        FR-06 & FreeRTOS task separation confirmed; control and UI tasks measured at 0\% CPU utilization during audio playback, confirming no interference with audio processing. & Pass \\
        \midrule
        EC-01 & Input protection verified by design; transistor clamping on gate inputs and rail-guarded opamp stages on CV inputs prevent ADC damage at full Eurorack signal range. & Pass \\
        EC-02 & See EC-01. & Pass \\
        EC-03 & AC-coupling and diode protection verified via loopback measurements. Initial attenuator values caused ADC saturation; resistor values corrected to yield $\qty{0.77}{V_{pp}}$ at codec input, within the \qty{\pm 0.53}{V} ADC input range. & Pass \\
        EC-04 & Power rails verified: \qty{5}{V} buck converter and \qty{3.3}{V} LDO operational; \qty{12}{V} rail retained for opamp stages. & Pass \\
        EC-05 & PCB layout follows analogue/digital separation guidelines. Quantitative noise measurements not yet completed. & Pending \\
        EC-06 & Mechanical dimensions conform to Eurorack 3U standard. & Pass \\
        \midrule
        FC-01 & DMA-driven audio verified; uninterrupted operation confirmed during CPU utilization measurements at full DSP load. & Pass \\
        FC-02 & FreeRTOS preemptive scheduling verified via CPU utilization measurements; audio task strictly separated from lower-priority tasks. & Pass \\
        FC-03 & Custom DSP chain implemented (tape-style sample engine, reverb); full chain utilizes 60--66\% CPU at \qty{48}{kHz}, leaving sufficient headroom. & Pass \\
        FC-04 & TLV320AIC3204 configured via I\textsuperscript{2}C at startup; audio exchanged over I\textsuperscript{2}S at \qty{48}{kHz}, 16-bit stereo. & Pass \\
        FC-05 & Flash persistence implemented for calibration data. & Pass \\
        \bottomrule
    \end{tabularx}
\end{table}

The majority of requirements were fully met. The two partial results (FR-03, FR-04) both stem from the same class of error: incorrect pin assignments during schematic entry, rather than fundamental design problems.
EC-05 remains pending due to incomplete noise measurements; subjective in-system testing showed no audible noise floor, but formal verification is deferred to a future revision.

\newpage
\subsection{Discussion of Limitations}

\subsubsection{Hardware Revision Defects}
Two pin misassignments were identified in this hardware revision that could not 
be corrected through firmware alone:
\begin{itemize}
	\item \textbf{Gate 03 input (FR-03):} The assigned pin PC9 does not support 
	EXTI interrupts simultaneously with the other assigned interrupt lines.
	A bodge wire was soldered directly between PC9 and PC6 on the MCU pins, 
	relocating the signal to a pin with full EXTI support, and the firmware was 
	updated accordingly.
	A PCB revision with the correct pin assignment is required to eliminate the bodge.
	\item \textbf{Slide potentiometer LEDs (FR-04):} PWM-capable timer channels 
	for the fader LEDs were incorrectly assigned during schematic entry, leaving 
	the slider LED indicators non-functional in this revision.
\end{itemize}

\subsubsection{Memory Headroom}
DTCMRAM utilisation stands at 98.5\% and main SRAM at 93\% in the current firmware build.
While sufficient for the implemented feature set, this leaves limited headroom for additional DSP algorithms or larger sample buffers.
The current recording and playback buffer holds \qty{2.5}{\second} of audio at $f_s = \qty{48}{\kilo\hertz}$, which is adequate for the tape-style use case but restrictive for longer recordings.

\subsubsection{Noise Characterisation (EC-05)}
Quantitative noise floor measurements have not been completed for this revision.
The analogue/digital separation strategy was applied during layout, but its effectiveness has not been formally verified through measurement.
During in-system testing in a Eurorack environment, the noise performance was subjectively sufficient and no audible noise floor was observed.

\subsubsection{Fixed-Point Phase Accumulator}
The playback engine uses a Q48.16 fixed-point phase accumulator, motivated by the concern that floating-point accumulation errors could cause phase drift over long playback durations (Section~\ref{sec:numerical-architecture}).
In retrospect, this concern does not apply to this system: the sample buffer holds only \qty{2.5}{\second} of audio at $f_s = \qty{48}{\kilo\hertz}$, meaning the playhead wraps within $2.5 \times 48000 = 120{,}000$ samples.
Floating-point rounding errors are on the order of $\epsilon \approx 10^{-7}$ per accumulation step; over 120,000 steps the accumulated error remains below $0.012$ samples -- well below the resolution of the interpolator.
Furthermore, the STM32H7 Cortex-M7 core includes a double-precision FPU, which provides 52 bits of mantissa and further reduces this already negligible error.
A \texttt{double} or \texttt{float} playhead would be fully sufficient and would eliminate the fixed/floating boundary at the interpolator input, improving code readability.
The fixed-point design is therefore a conservative choice that is correct but unnecessary for this buffer size, and could be simplified in a future refactor.

\subsubsection{Input Stage Low-Frequency Rolloff Discrepancy}
The measured \SI{-3}{\decibel} cutoff frequency of the audio input high-pass filter is approximately \SI{37.6}{\Hz}, compared to a theoretical value of \SI{1.8}{\Hz} calculated from the AC-coupling network ($R_{in} = \SI{40}{\kilo\ohm}$, $C_3 = \SI{2.2}{\micro\farad}$).

The root cause has not been identified within the scope of this project, as only an end-to-end frequency response measurement was conducted.
To isolate the source, individual frequency response measurements of the input and output stages should be performed separately in a future revision.
Practically, the measured cutoff is reaching into the audible low frequency end, as sub-bass frequencies do reach the lower \qty{30}{Hz}.
Still this rolloff is marginally a and the device is usable for musical applications.